% \documentclass[11pt]{letter}
\documentclass{letter}
\usepackage[utf8]{inputenc}
% \usepackage{ngerman}
\usepackage[english]{babel}
%\usepackage{enumerate}
%\usepackage{eurosym}
%\lochermarke
%\faltmarken
%\fenstermarken
%\trennlinien    

\usepackage{address}

\begin{document}
\begin{letter}{Lucerne University of Applied Sciences and Arts\\
Sascha Götte\\
Technikumstrasse 21\\
6048 Horw}
\opening{Dear Mr. Götte}
In an English language newspaper I came across your advertisement for people 
to work for the International winter school on "`'Design Thinking"'. As I was 
tutor for the module electrotechnics 1 at Lucerne University of Applied 
Sciences and Arts last semester, I have some experience working with students. 
About four times a year I \emph{give} courses for students from secondary 
school. In this courses they learn to know four different professions from a 
technical environment. I take part as teacher for the electronics technician. 
I love to teach the students what an electronics technician does. I achieved 
the First Certificate in English in 2010. Since then I took no English class. 
But I use English sometimes for my actual job when engineers from abroad 
arrive to test our devices. Currently I am studying electrotechnics at the 
Lucerne University of applied Sciences and Arts. This semester I take part 
in the cource FCE. 

I hope to hear from you soon and get the chance to meet you at an interview. 
%
\closing{Kind regards, }
%
\end{letter}
\end{document}

%\endinput     